---
title: <font size = "8">Usage of Water Bottle Filling Stations on the Johns Hopkins University Homewood Campus</font>
author: "John Lin"
date: "6/24/2020"
output: ioslides_presentation
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(leaflet)
data <- read.csv("data.csv", check.names = FALSE)
```

## Background

Johns Hopkins University is committed to sustainable water systems.

Beginning in 2013, over 60 water bottle filling stations were installed on Homewood campus. 

This Shiny app examines the usage of the water bottle filling stations on Homewood from 2016 to 2019.

## Shiny app

This Shiny app contains 4 tabs:

* **About this site.** Background information and instructions on how to navigate the site.

* **Data.** A data spreadsheet showing the bottle count for each filling station at each year.

* **Map.** A map showing the water bottle filling stations on Homewood campus. The user can use the dropdown menu to select a year to display.

* **Time plot.** A time plot showing the bottle counts from 2016 to 2019. The user can choose from a group of checkboxes to select the building types to display.

## Example R code: Map

```{r, echo = TRUE, results = "hide", message = FALSE}
pal <- colorFactor(
    palette = c("red", "darkgreen", "blue"),
    levels = c("Lecture hall", "Residence hall", "Other")
  )
my.map <- data %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(weight = 3, radius = sqrt(data[,8]/200),
                   color = ~pal(data$`Building Type`),
                   popup = paste("<strong>", data$Location, "</strong>", "<br/>",                                  "Bottle Count (2019): ", data[,8], sep = "")) %>%
  addLegend(labels = c("Lecture hall", "Residence hall", "Other"),
            col = c("red", "darkgreen", "blue"))
```

## Example output: Map
```{r}
my.map
```